---
title             : "Results"
shorttitle        : "Results"

author: 
  - name          : "Caspar J. van Lissa"
    affiliation   : "1,2"
    corresponding : yes    # Define only one corresponding author
    address       : "Padualaan 14, 3584CH Utrecht, The Netherlands"
    email         : "c.j.vanlissa@uu.nl"

affiliation:
  - id            : "1"
    institution   : "Utrecht University faculty of Social and Behavioral Sciences, department of Methodology & Statistics"
  - id            : "2"
    institution   : "Open Science Community Utrecht"


authornote: |

abstract: |

keywords          : "keywords"
wordcount         : "X"

bibliography      : ["r-references.bib"]

floatsintext      : no
figurelist        : no
tablelist         : no
footnotelist      : no
linenumbers       : yes
mask              : no
draft             : no

documentclass     : "apa6"
classoption       : "man"
output: papaja::apa6_docx
---

```{r setup, include = FALSE}
run_everything <- TRUE

library("papaja")
if(!require(motley)){
  library(devtools)
  install_github("cjvanlissa/motley")
  library(motley)
}
library(metafor)
library(metaSEM)
if(file.exists("table23.csv")) file.remove("table23.csv")
if(run_everything){
  source("data_cleaning.R")
}

source("data_preprocessing.R")
source("clean_moderators.R")
source("pool_correlation_matrices_robust_se.R")
pool_correlation_matrices()
pool_correlation_matrices("age_group")
pool_correlation_matrices("p_cluster")
pool_correlation_matrices("same_wave")
source("fit_models.R")
source("fit_models_age_group.R")
source("fit_models_parenting_cluster.R")
source("fit_models_wave.R")
load("pooled_Overall.RData")
```

```{r analysis-preferences}
# Seed for random number generation
set.seed(42)
knitr::opts_chunk$set(cache.extra = knitr::rand_seed)
# To re-run the multigroup analysis:
# source("data_wrangling_multigroup.R")
# source("multigroup_model_constraints.R")
#load("subgroups.RData")
#load("results_multigroup.RData")
#load("par_tables.RData")
#load("metafor_t_test.RData")
```



# Analysis

We used meta-analytic structural equation modeling [@cheung2015meta] to
address two
related research questions: Whether behavior similarly affects teacher-student
and peer relationships, and whether teacher-student relationships explain the
association between behavior and peer relationships. Following the
two-stage procedure[see also @cheung2015meta] , we first pooled correlations across studies,
and obtained the asymptotic sampling covariance matrix. 
We used robust variance estimation with bias-reduced
linearization adjustment to account for the fact that several studies
reported multiple effect sizes
[@pustejovskySmallSampleMethodsClusterRobust2018].
Then, a SEM-model was 
fit to the pooled correlation matrix. 

Three subsamples can be identified in the data, based on the time lag between
variables. Behavioral problems, being the primary exogenous variable, were
always coded at time 1. For one group of studies, peer-relationship and 
teacher-student relationship quality were also coded at time 1. This subset
of studies will be referred to as the *cross-sectional* sample. For another 
subset, teacher-student relationship quality was coded at time 1, but 
peer-relationship quality was coded at a later time. This allows us to estimate
time-lagged relationships from behavior and teacher-student relationship 
quality, to peer relationship quality. This subset will be referred to as the
*teacher-first* sample. Finally, in a third subset, which will be referred to as
the *peer-first* sample, teacher-student relationship was coded at a later time
than the other variables.

## Estimating the total N per sample

The N for each effect size was not
coded unambiguously. Specifically, metaSEM requires one N for each correlation
matrix, but in our data, N was coded per correlation coefficient. 
Furthermore, our data included many studies with multiple effect sizes. It was 
not always clear whether these effect sizes originated from the same sample.
We computed <!--two alternative estimates for the
total N across
studies: A--> a lower bound estimate for N, which assumed that each study was
based on only
a single sample, and consisted of the sum the smallest sample size coded for
each study ID. <!--A more liberal estimate summed the unique sample sizes coded for
each study; the underlying assumption being that correlations derived from the
same sample would have been 
reported as having the same N. However, sensitivity analyses indicated that 
there were no differences in results between these two estimates of N, at least
to the third decimal. We used the lower bound estimate of N to err on the side
of caution.-->
The estimated total sample size was ....



\newpage

# References
```{r create_r-references}
#lapply(paste('package:',names(sessionInfo()$otherPkgs),sep=""),detach,character.only=TRUE,unload=TRUE)
#library(metafor)
##library(papaja)
#library(metaSEM)
#library(robumeta)
#r_refs(file = "r-references.bib")
```

\begingroup
\setlength{\parindent}{-0.5in}
\setlength{\leftskip}{0.5in}

<div id = "refs"></div>
\endgroup
